### 2020-05-07 README.Rmd
typo

>>>>

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
[![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
<!-- badges: end -->
